This is the title [Article v\versionnumber]

### 2022-09-13 manuscript/manuscript.tex
Update manuscript.tex
update on double counting
Added WIP cheatsheet

When calculating the total $E_{ww}$ of the system, double-counting of interactions must be avoided. For a given region $\bold{R}$, the contribution
from the interaction of  water molecules outside $\bold{R}$ with the water molecules inside $\bold{R}$ is accounter for in $E_{ww}$. This means that
the sum of $E_{ww}$ of two different regions, $\bold{R_1}$  and $\bold{R_2}$, taken from the same simulation box will not be equal 
to the union of $E_{ww}$ of the two regions due to double-counting.

Double-counting is accounted in two different ways. The first method uses the water-displacement method. This method is applicable when determining the energetic cost of kicking out a water molecule. For example, when a ligand binds to the protein, water molecules will be displaced from the binding pocket to
the bulk.

@@

The second method uses normalized water properties to account the difference in water properties of two different regions. 
The normalized water property is defined as the water property per water molecule.

@@

@@

\paragraph{Postprocessing and Analyzing GIST results}
Cppraj outputs the quantities calculated in a data explorer "DX" file format which can be easily visualized in Pymol or VMD.
Aside from the thermodynamic quantities, GIST also calculates the number densitiies of hydrogen and oxygen in each voxel. Here is a full list of quantities calculated by GIST \todo{This is incomplete!}:

@@

It has been shown in literature \cite{Chen2021,Waibl2022-gist-solvents} that the total solvation entropy in water is best approximated by 0.6 times the first order entropy.
Also compute the scaled entropy and check the effect on the binding affinity.
The expected results are summarized in Table~\ref{tab_dg_monomers_dimer}.
%\todo{Table 1 is placed quite akwardly at the moment for me, maybe enforce its position? -vah. Ok? -fwa}
\begin{table}[h]
	\caption{Free energy contributions for the monomers and the dimer.}\label{tab_dg_monomers_dimer}
	\small
	\begin{tabular}{lrrrrr}
		\toprule
		System       & E(internal) & $\Delta E^\textit{GIST}$ & $\Delta S^\textit{GIST}$ & $\Delta S^\textit{scaled}$ & total \\
		\midrule
		complex      & -1303.4 & -361.2 & -233.1 & -139.9 & -1524.7 \\
		streptavidin & -1180.7 & -360.8 & -242.4 & -145.4 & -1396.1 \\
		biotin       & -24.0   &  -98.1 &  -35.1 &  -21.1 &  -101.0 \\
		Diff         & -98.7   &   97.7 &   44.4 &   26.6 &   -27.6 \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\section{Recent developments}
\subsection{GIST with non-water solvents}
\subsection{GIST with salt-water mixtures}

>>>>

When computing the total $E_{ww}$ of the system, double-counting of interactions must be avoided.
The total solvent-solvent energy of the system is as follows:

@@

However, when water is replaced from a small region $R$ of interest, such as a single water molecule, almost all interactions are with water molecules outside of this region.
Therefore, there is no double counting, and the full solvent-solvent energy should be used.

@@

When the region of interest $R$ comprises more than one molecule, interactions within this region are double-counted while interactions to the outside are not.
To take this into account, the solvent-solvent energy between each pair of voxels $E_{ww,kl}$ is needed.
While this is supported by the standard GIST implementation, it is rarely done due to the large size of the $E_{ww,kl}$ matrix.

We note that replacement of a small or medium solvent region would lead to reorganization of the surrounding solvent.
However, this depends on the local environment and on \emph{what} the molecule would be replaced by.
Therefore, the effect of reorganization can not be directly included in the GIST method, but must be judged for each case individually.
This is not a problem when computing the total free energy of solvation $\dgsolv$, since no additional boundary is created.
\todo{This is a bit unclear to me, could we elaborate on this a bit more? What are we asking of the reader here, how would one consider this effect? -vah}

@@

\paragraph{Postprocessing and Analyzing GIST results}
Cpptraj outputs the quantities calculated as a "open data explorer" (.dx) file format which can be easily visualized in Pymol or VMD.
Aside from the thermodynamic quantities, GIST also calculates the number densities of hydrogen and oxygen in each voxel. Here is a full list of quantities calculated by GIST \todo{This is incomplete!}:

@@

It has been shown in literature \cite{Chen2021,Waibl2022-gist-solvents} that the total solvation entropy in water is best approximated by 0.6 times the first order entropy.
Also compute the scaled entropy and check the effect on the binding affinity.
The expected results are summarized in Table~\ref{tab_dg_monomers_dimer}.
%\todo{Table 1 is placed quite akwardly at the moment for me, maybe enforce its position? -vah. Ok? -fwa}
\todo{this table is super confusing to me. What's "total"? Doesn't seem to be E-TS. Diff is also not the sum of other total entries. Shouldn't it be TS instead of S?-vah}
\begin{table}[h]
	\caption{Free energy contributions for the monomers and the dimer in kcal$\cdot$mol$^{-1}$.}\label{tab_dg_monomers_dimer}
	\small
	\begin{tabular}{lrrrrr}
		\toprule
		System       & E(internal) & $\Delta E^\textit{GIST}$ & $\Delta S^\textit{GIST}$ & $\Delta S^\textit{scaled}$ & total \\
		\midrule
		complex      & -1303.4 & -361.2 & -233.1 & -139.9 & -1524.7 \\
		streptavidin & -1180.7 & -360.8 & -242.4 & -145.4 & -1396.1 \\
		biotin       & -24.0   &  -98.1 &  -35.1 &  -21.1 &  -101.0 \\
		Diff         & -98.7   &   97.7 &   44.4 &   26.6 &   -27.6 \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\section{Recent developments}
\subsection{GIST with non-water solvents}
\subsection{GIST with salt-water mixtures}
\section{Cheatsheet}
%This will be a cheatsheet containing all options for cpptrajs GIST implementation
\subsection{Installation}
GIST calculations in cpptraj can be sped up through various levels of parallelization. When cpptraj was compiled with the '-cuda' configure flag set, the GPU accelerated version of GIST is used automatically.

\subsection{The CPPTRAJ action}
\subsection{Output}
GIST calculations put out a variety of data sorted by voxel into a file specified by the "out" keyword. Some of the output data is also automatically written to "open data explorer" (.dx) files for convenient visualisation in software such as VMD or PyMOL. The following columns can be found in the output file:
\begin{tabular}{l l p{.3\textwidth}}
\toprule
gX & X & For every element in the main solvent, the number density of atoms found in the voxel, in units of the bulk density. If the same element occurs multiple times, the bulk density is scaled accordingly. \\
Esw & X &  Mean solute-water interaction energy density. \\
Eww & X & Mean water-water interaction energy density. \\
PME & [pme] & Water PME energy density. \\
U\_PME & [pme] & Water PME energy density. \\
dTStrans & X & First order translational entropy density. \\
dTSorient & X & First order orientational entropy density . \\
neighbor & X & Mean number of waters neighboring the water molecules found in this voxel multiplied by the voxel number density. \\
dipole & X & Magnitude of mean dipole moment (polarization). \\
order & X & (if \inlinecode{doorder} was specified) Average Tetrahedral Order Parameter. \\
dipolex & X & x-component of the mean water dipole moment density \\
dipoley & X & y-component of the mean water dipole moment density \\
dipolez & X & z-component of the mean water dipole moment density \\
Eij & X & (if \inlinecode{doeij} was specified) Water-water interaction matrix. \\
\bottomrule
\end{tabular}
